Comparing vector-based and ACT-R memory models of tag retrieval:\protect\\User-customized hashtag/tag prediction on Twitter and StackOverflow

### 2014-07-23 writeups/dissertation/dissertation.tex
foo

@@

Overall, both the random-permutation and Bayesian models fit the observed tagging behavior in StackOverflow and Twitter relatively well.
Given that the storage space required to represent the co-occurrences for the random-permutation is dramatically smaller than the uncompressed Bayesian model,
and that the compression is lossy and essentially random (i.e., no SVD),
it is quite interesting that the random-permutation model performs nearly as well as the full Bayesian model for this task.

>>>>

Overall, both the random-permutation and Bayesian declarative memory models fit the observed tagging behavior in StackOverflow and Twitter relatively well.
These results provide support that choosing a hashtag when composing a tweet and tagging a StackOverflow post is a long-term memory retrieval process.
However, both models were not 100 percent accurate, and the amount of variance left to predict was much larger than what would be observed if retrieval noise was included in the model.
So is most likely the case that the task is not done solely with declarative memory processes.

Or, perhaps authors are taking advantage of context information that is not currently represented in the model.
For example, time of day might be a useful predictor of tag use.
\textcite{Cohn2012} built a tag-prediction model that was based primarily on temporal cycles of tag use.
This technique could be naturally incorporated into a co-occurrence framework by including time of day as an additional context by tag co-occurrence for each post.
This would allow time of day information to be used alongside the rest of the context information in the words of the post.
A similar technique could be used to add additional context predictors to the model.
These co-occurrences could either be added on as additional columns to the existing co-occurrence matrix,
or a separate co-occurrence matrix could be used for each additional context component, similar to how separate matrices and context predictors were created for the words in the title and body of a post. 
Including additional context predictors such as time of day may help improve model accuracy,
and perhaps it is the case that the rest of the variance left to predict is from these context components that the author is using but are not yet included in the model.
That is, perhaps this tagging process is completely declarative, and the remaining cues that the author is using are yet to be discovered.

\tectcite{Anderson1991} also used tasks similar to tag use on StackOverflow and Twitter when deriving the prior component of the declarative memory theory.
\citeauthor{Anderson1991} examined, for example, the frequency of word choice over time used for the title of articles for the New York Times,
and used the results to derive the power law equation for the prior term in the declarative memory model.
ACT-R's declarative memory theory claims that the system has evolved to make predictions that closely match the statistical structure of the environment.
Using a power-law equation to model future tag use based on past tag use is a reasonable statistical approach to the problem.
It is also the case that this same equation is an accurate model for the prior component of declarative memory, as was shown by \citeauthor{Anderson1991} in the original derivation, 
and as is supported in the results from this study.

@@

Given that the storage space required to represent the co-occurrences for the random-permutation is dramatically smaller than the uncompressed Bayesian model,
and that the compression is lossy and essentially random (i.e., no SVD),
it is quite interesting that the random-permutation model performs nearly as well as the full Bayesian model for this task.
